---
title: "Calculating Mean Arterial Pressure"
author: "Athanasia Monika Mowinckel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculating Mean Arterial Pressure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This scripts requires the existance of measurements of diastolic and systolic blood pressure, and calculates the Mean Arterial Pressure (MAPmean).

This script uses the following calculation for MAP mean

$$ MAP = \simeq \frac{(2 \times DP) + SP}{3} $$

## Input:

**IN  =  data frame**
A dataframe including the following columns (MOAS columns): 

 - CrossProject_ID
 - Subject_Timepoint
 - BloodPress_Diastolic_1
 - BloodPress_Diastolic_2
 - BloodPress_Systolic_1
 - BloodPress_Systolic_2

## Output: 
Returns the entire data frame that was provided, with the addition of the MAPmean column


## Invoking function 

```{r warning=F, message=F, eval=FALSE}

calc_map_mean(data)
```
